Paper \#ZW10157

### 2018-12-21 paper/submission/ZW10157-response-1.tex
fixing figure names in paper

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}

@@

We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.\ The details can be found in the following pages.

>>>>

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

@@

We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.
The details can be found in the following pages.
